---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{advanced_google}
%\VignetteDepends{xtable}
-->

##Deep feature search with pairs##

<br>
Goal: identify dependencies across variables and time series (Google Stock)
<br>
```{r advanced_google_1, eval=TRUE, results='asis'}
googleStock = getData("googleStock")
print(xtable(head(googleStock,n=5)), type='html', comment=F)
```
<br>
The target variable reflects if the google closing price today was more than the closing price at a critical time point in the past.
Let's split the data sequntially and first try a regular model at depth = 2
```{r advanced_google_2, eval=TRUE, results='asis'}
googleTrainTest = trainTestSplit(googleStock)
```
<br>
```{r advanced_google_3, eval=TRUE, message=FALSE, results='hide'}
googleModel = learn(
	projectName = "googleStock",
	trainData = googleTrainTest[[1]],
	testData = googleTrainTest[[2]],
	target = "happy",
	featureGenerationCtrl = featureGenerationControl(
	 		maxFeaturesCount = 50
	)
)
googleModelEval = googleModel$evaluate()
```

```{r advanced_google_4, eval=TRUE, results='asis'}
print(xtable(googleModel$features()[1:5,c("idx","feature")]), type='html', comment=F) 
```

```{r advanced_google_5, eval=TRUE, echo=TRUE, cache=FALSE}
e=googleModel$evaluate()$summary
```

Now let's enable a deep feature search using an advanced feature search with pairs.
```{r advanced_google_6, eval=TRUE, message=FALSE, results='hide'}
googleModelAdvanced = learn(projectName = "googleStockAdvanced",
    trainData = googleTrainTest[[1]],
    testData = googleTrainTest[[2]],
    target = "happy",
	 	featureGenerationCtrl = featureGenerationControl(
	 				featureSearchMode = "ADVANCED_WITH_PAIRS",
 					maxFeaturesCount = 50,
	 				maxFeatureDuration=5
	 	)
)
```

```{r advanced_google_7, eval=TRUE, results='asis'}
print(xtable(googleModelAdvanced$features()[1:1,c("idx","feature")]), type='html', comment=F) 
```
```{r advanced_google_8, eval=TRUE, echo=TRUE, cache=FALSE}
e=googleModelAdvanced$evaluate()$summary
```

