---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{basic_regression}
%\VignetteDepends{xtable}
-->
  
##Basic regression##
<br>
<br>

####Overview####

Goal: Predict Titanic Passenger
<br>
This example demonstrates how to perform a simple regression using the SparkBeyond platform.
We will use the same titanic data but now we will aim to predict the column `age`.
<br>

####Training data####

Here are all the columns available:
```{r basic_classification_1, results='asis'}
data = getData("titanic_train")
#View(data) # in order to view the data in an RStudio tab
print(xtable(data[1:5,]), type='html', comment=F)
```
<br>
<br>

####Pipeline####

The problem was automatically identified as a regression problem because the target is continuous.
<br>
```{r basic_regression_2, eval=TRUE, message=FALSE, results='hide'}
titanicAgeModel = learn(
	projectName = "titanic_age",
	trainData = data,
	target = "age"
)
```
<br>
<br>

####Top features####

From this example, we can see that having the tokens 'master' and 'miss' in the passenger name are strong indicators of the gender. 
<br>
```{r basic_regression_3, eval=TRUE, results='asis'}
library(xtable)
print(xtable(titanicAgeModel$features()[1:20,c("idx", "feature")]), type='html', comment=F)
```

