---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{context_tweets}
%\VignetteDepends{xtable}
-->

##Context - terms map - sentiment analysis##

Goal: Identify sentiment in twitter tweets.
<br>

###Tweets sentiment ###

```{r context_tweets_1, eval=TRUE, message=FALSE, results='hide'}
tweets = getData("tweets_sentiment")
SentimentModel = learn(
		projectName="tweets",
		trainData=tweets,
		target="sentiment",
		featureGenerationCtrl = featureGenerationControl(maxFeaturesCount = list(50)),    
		modelBuildingCtrl = modelBuildingControl(algorithmsWhiteList = list("RRandomForestClassifier")),  
		autoSave = FALSE
)
SentimentEval = SentimentModel$evaluate()
```
<br>
In this example we load a sentiment dataset with a tweet column and a setiment target (-1 or 1). The top feature is a textSentimentScore which is automatically computed.

```{r context_tweets_2, eval=TRUE, results='asis'}
print(xtable(SentimentModel$features()[1:10,c("idx","feature")]), type='html', comment=F)
```
```{r context_tweets_3, eval=TRUE, echo=TRUE, cache=FALSE}
SentimentModelEval = SentimentModel$evaluate()
```
<br>

###Tweets with a context dataset that creates a terms map###

```{r context_tweets_4, eval=TRUE, message=FALSE, results='hide'}
tweets = getData("tweets_sentiment")
SentimentModelContext = learn(
		projectName = "tweets",
		trainData = tweets,
		target = "sentiment",
		contextDatasets = list(contextObject(data = getData("sentiment_lexicon"), name = "sentiment_lexicon")),
		featureGenerationCtrl = featureGenerationControl(maxFeaturesCount = list(50)),    
		modelBuildingCtrl = modelBuildingControl(algorithmsWhiteList = list("RRandomForestClassifier")),
		autoSave = FALSE    
)
```
<br>

In order to improve performance we can include a custom context Dataset. The sentimentLexicon includes over 6000 single words with a either a positive or negative sentiment. The top features now are actually derived by looking up the values in the lexcion (data_column) and the classificaiton performance is boosted.

```{r context_tweets_5, eval=TRUE, results='asis'}
print(xtable(SentimentModelContext$features()[1:10,c("idx","feature")]), type='html', comment=F) 
```

```{r context_tweets_6, eval = FALSE, message=FALSE}
writeLines(readLines(paste0(SentimentModelContext$artifact_loc,"/reports/features/features_trace.txt"),n=9))
```
```{r context_tweets_7, eval=TRUE, echo=TRUE, cache=FALSE}
SentimentContextEval = SentimentModelContext$evaluate()
```
