---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Example 1}
%\VignetteDepends{xtable}
-->

```{r, echo=FALSE, eval = TRUE, message=FALSE, results='hide'}
library(SBadapter)
setSBserverIOfolder("~/devel/localdata")
```
  
# Example 1 - simple classification#    
Goal: Predict Titanic Passenger Survival
<br>
This example demonstrates how to perform a simple classification using the SparkBeyond platform.
We will use data from the famous Kaggle competition to predict who will die on the Titanic.
We can get the titanic train data by calling `data = getData("titanic_train")`. The column `survived` contains the information for whether a Titanic passenger survived.
In the following example we ask the engine to create and return the top 25 features.  
<br>
Data sample:
```{r titanic_sample_data, results='asis'}
library(xtable)
print(xtable(getData("titanic_train")[1:5,]), type='html', comment=F)
```
<br>
```{r titanic_survived_simple, eval=TRUE, message=FALSE, results='hide'}
data = getData("titanic_train")
titanicSurvivedModel = learn(projectName = "titanic_survived",
                        trainData = data,
                        target = "survived",
                        algorithmsWhiteList = list("RRandomForestClassifier"),  
                        maxFeaturesCount = 25,  # number of feature counts to check (if a list is provided
                                                # the best will be selected using cross validation)
                        scoreOnTestSet = TRUE,  # will create lift plots and prediction table 
                        autoSave = FALSE        # in order to avoid automatically creating a local object 
                                                # pointing to the created model
                    )
```
<br>
On the Titanic most children and women were rescued first, hence had higher survival rates.
The first feature that was generated, breaks down the `name` column into tokens and notes that the token "mr" is not included in the passenger name. This feature effectively identifies both the children and women populations.

Here are the top 3 features (each contains a lift signal pointing to which class each feature suggests):
```{r, eval=TRUE, results='asis'}
print(xtable(titanicSurvivedModel$features()[1:3,c("idx", "feature", "Lift.0", "Lift.1")]), type='html', comment=F)
```
<br>
To view an html report with all the information on the features (on train or test) run:
```{r, eval = FALSE, message=FALSE}
titanicSurvivedModel$showFeaturesTrain()
titanicSurvivedModel$showFeaturesTest()
```
  
To view the feature trace report review /reports/features/features_trace.txt
```{r, eval = TRUE, message=FALSE}
writeLines(readLines(paste0(titanicSurvivedModel$artifact_loc,"/reports/features/features_trace.txt"),n=9))
```

```{r, echo=FALSE, eval = FALSE, message=FALSE}
file.copy(paste0(titanicSurvivedModel$artifact_loc,"/reports/predictions/test/Lift_plot_survived_1.html"), getwd()) 
```
<!-- 
need to find a way to link it to "/Library/Frameworks/R.framework/Versions/3.1/Resources/library/SBadapter/extdata/" or externally (amazon?) or generate equivalent figure
<iframe width="400" height="400" src="./Lift_plot_survived_1.html" frameborder="0" seamless></iframe>
-->
