---
output:
  knitrBootstrap::bootstrap_document:
    title: "Examples"
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{All examples}
-->

<!-- 
  Comment:
  ========
  Set eval = FALSE (with spaces) in places that you would like not be to evaluated permanently (i.e., not be capture by the replace all) 
  Use cache = TRUE to prevent recalculations => stored  per chunk identifier.
  
  To geneate examples:
  library(knitrBootstrap)
	library(rmarkdown)
	render('./SparkBeyond/inst/extdata/examples-master.rmd', 'knitrBootstrap::bootstrap_document')
--> 

<!-- 
Write text for all examples
Show sampling, grouping examples - in a different section
Show predict / create package etc example - should be in a different section
-->

#Spark Beyond Package Examples#

<br>

#A. Basic modeling#
```{r basic_classification, child='basic_classification.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>
```{r basic_regression, child='basic_regression.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

#B. Basic feature generation controls#

```{r featureGeneration_featureExclusions, child='featureGeneration_featureExclusions.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

#C. Using SparkBeyond knowledge#

```{r external_weather, child='external_weather.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

#D. Model with complex data structures#

##Coming soon.##

<br>
<br>

#E. Add context to modeling#

```{r context_tweets, child='context_tweets.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>
```{r context_geoSpatial, child='context_geoSpatial.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>


#F. Time series analysis#

```{r timeSeries_timeWindow, child='timeSeries_timeWindow.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

```{r timeSeries_frequency, child='timeSeries_frequency.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

#G. Advanced feature controls#

<br>
<br>
```{r advanced_google, child='advanced_google.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>
```{r advanced_complexSum, child='advanced_complexSum.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>
```{r advanced_crossRow, child='advanced_crossRow.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>
```{r advanced_customFunctions, child='advanced_customFunctions.rmd', eval = TRUE, cache=TRUE}
```
<br>
<br>

#H. Unsupervised learning#

<br>
<br>

##Coming soon.##

<br>
<br>
<br>
<br>

#I. More info#

<br>
<br>
For more information please check:

 * `tutorial()`   : [Getting started tutorial](https://s3.amazonaws.com/public-sparkbeyond/tutorial.html)
 * `examples()`   : [These examples](https://s3.amazonaws.com/public-sparkbeyond/examples-master.html)
 * `SBhelp()`       : [html help of this package](https://s3.amazonaws.com/public-sparkbeyond/SBadapterDocs/index.html)
 * `faq()`        : [Frequently Asked Quetions](https://docs.google.com/document/d/1MfUduRR2jZiLaZPfc8Q68ijvWctjNKgg7smeqEoH9yk/pub) 
 * `reportsList()`: [explantion of all the reports produced by the SparkBeyond engine](https://docs.google.com/document/d/16ogU45DHrW0x_BVLS5TiyPMblORUGSxaScR8i_lIDI0) 
 * `resources()`  : [various SparkBeyond resources](https://docs.google.com/document/d/1wF7EkdyEB8409blpkianOyQxvi-OWasVEGegdLk-MOI/pub)
