---
output:
  knitrBootstrap::bootstrap_document:
    title: "Tutorial"
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{tutorial}
-->

#SparkBeyond R package tutorial#

<br>
<br>

#Installation#
 
<!-- 
  Comment:
  ========
  eval should always be FALSE here. I set eval = FALSE with spaces so that it won't be found in replace all 
--> 
  
```{r, eval = FALSE, message=FALSE, results='hide'}
install.packages("devtools")
devtools::install_github('zinman/SparkBeyond')
library('SparkBeyond')
```
```{r, echo=FALSE}
library('SparkBeyond')
```

<br>
<br>

#Login#
```{r, eval = FALSE, message=FALSE, results='hide'}
login('username','password','domain')
```

<br>
<br>

#Project structure#

Learning sessions are associated with a project name (specified as a parameter to the learn function, see below).
<br>
A serial revision number will be assigned to each learning session. Each revision contains the complete artifact for a rearning result, including reports, model code, model binaries, and required resources.
The complete list of reports is available `reportsList()`: [explantion of all the reports produced by the SparkBeyond engine](https://docs.google.com/document/d/16ogU45DHrW0x_BVLS5TiyPMblORUGSxaScR8i_lIDI0)
<br>
<br>

#Feature search + Model building #
`learn` is used to discover features & build a model, it requires the following input:

1.  `projectName`         - a name describring the analysis.  
2.  `trainData`           - a data frame
3.  `target`              - the column name in the input data denoting the label to learn


```{r, echo=FALSE, message=FALSE, results='hide'}
setSBserverIOfolder("/tmp/")
```

```{r tutorial_basic_example, eval=FALSE, cache = TRUE}
train = getData("titanic_train")
model = learn(
	projectName = "titanic",
  trainData = train,
  target = "survived"
)
```

The returned `Session` object named `model` encapsulates a predictive-model on which we can perform various operations.

<!-- 
  Comment:
  ========
  The help file for `model` class contains additional information. 
--> 

<br>
<br>

#Enriching a dataset #

`enrich` adds new features to a `dataset` using a `model`, it requires the following input:

1.  `data`          - a data frame
2.  `featureCount`  - number of features  (use `NA` to get all features)

```{r, echo=FALSE}

```

```{r,  eval=FALSE}
test = getData("titanic_train")
enriched = model$enrich(data = test, 
             featureCount=10)
```

Each feature is added to the dataset as a new column

```{r,  eval=FALSE}
colnames(enriched)
```

As you can see we now have 10 original *titanic* columns + 10 additional columns generated by the model. 

<br>
<br>

#Making a prediction #

`predict` is used to calculate predicted-values for `target` based on a `model` applied to a `dataset`, 

it requires the following input:

1.  `data`       - a data frame

```{r,  eval=FALSE}
predicted = model$predict(data = test)
```

The resulting prediction is added to the `dataset` as a set of new columns

```{r,  eval=FALSE}
colnames(predicted)
predicted[1:5,c("survived_predicted", "probability_0", "probability_1")]
```

We now have 3 additional columns:

1. final prediction
2. probability of class "0"
3. probability of class "1"

<br>
<br>

#Model evaluation #

`evaluate` summarizes `model` results in a short textual report. 

```{r,  eval=FALSE}
eval = model$evaluate()
```
It also returns an `eval` object containing evaluation metrics.

<br>
<br>

#Reports #

A rich set of pre-defined reports is available for feature & model analysis. 
These are HTML reports and will show either in the RStudio viewer pane or in an external browser. 

##Data & Features ##
* `showInputSchema` - Schema of the dataset sent for modeling
* `showFeaturesTrain` - Features discovered by the system in the learning process 
* `showFields` - Fields from which features were generated 
* `showFunctions` - Transformations used to generate the features
* `showExtractors` - Extractors used to generate the features

##Model ##
* `showReport` - Show a specific report
* `showConfusionMatrix` - Confusion matrix  (option for a normalized version)
* `showModelComparison` - Comparison evaluation table of the various algorithms attempted

<br>
<br>

##Examples ##

Here are a few examples:

###Features ###
```{r,  eval = FALSE}
model$showFeaturesTrain()
```
<iframe width="900" height="400" src="https://3ceaeb28a951bf57d68ca32211bb4c98dd31f5fc.googledrive.com/host/0Byt-OjYvY171fnJIS25JTmZxQ2RqMzc5dlFQZTNiaVZ1bXpqWGxiRDVsSWlzTEpUbU5lMjg/SB_Rplugin/img/features.html"  frameborder="0" seamless></iframe>

### Confusion matrix ###
```{r,  eval = FALSE}
model$showConfusionMatrix()
```
<iframe width="400" height="400" src="https://3ceaeb28a951bf57d68ca32211bb4c98dd31f5fc.googledrive.com/host/0Byt-OjYvY171fnJIS25JTmZxQ2RqMzc5dlFQZTNiaVZ1bXpqWGxiRDVsSWlzTEpUbU5lMjg/SB_Rplugin/img/confusionMatrix.html"  frameborder="0" seamless></iframe>

### ROC plot ###
```{r,  eval = FALSE}
model$showReport(report_name ="model/roc_best_0.html")
```
<iframe width="1000" height="800" src="https://3ceaeb28a951bf57d68ca32211bb4c98dd31f5fc.googledrive.com/host/0Byt-OjYvY171fnJIS25JTmZxQ2RqMzc5dlFQZTNiaVZ1bXpqWGxiRDVsSWlzTEpUbU5lMjg/SB_Rplugin/img/roc_best.html"  frameborder="0" seamless></iframe>

### Performing feature search only ###
There is an option to perform only feature discovery at the learning stage using `featureSearch`

```{r, eval = FALSE}
model = featureSearch(projectName = "titanic",
                        trainData = train,
                        target = "survived")
```
In this case, the user will be able to call `evaluate` but will get an exception when calling `predict`.

In addition, some of the reports pertaining to model evaluation (e.g., `showReport` and `showConfusionMatrix`) will not be available.  

<br>
<br>

#Saving and loading models #
 
Models can be saved using regular R `load()` and `save()` methods. By default, the result of each learning session is saved into the current directory.

<br>
<br>

#More info#
For more information please check:

 * `tutorial()`   : [this tutorial](https://s3.amazonaws.com/public-sparkbeyond/tutorial.html)
 * `examples()`   : [html page with various examples](https://s3.amazonaws.com/public-sparkbeyond/examples-master.html)
 * `SBhelp()`       : [html help of this package](https://s3.amazonaws.com/public-sparkbeyond/SBadapterDocs/index.html)
 * `faq()`        : [Frequently Asked Quetions](https://docs.google.com/document/d/1MfUduRR2jZiLaZPfc8Q68ijvWctjNKgg7smeqEoH9yk/pub) 
 * `reportsList()`: [explantion of all the reports produced by the SparkBeyond engine](https://docs.google.com/document/d/16ogU45DHrW0x_BVLS5TiyPMblORUGSxaScR8i_lIDI0) 
 * `resources()`  : [various SparkBeyond resources](https://docs.google.com/document/d/1wF7EkdyEB8409blpkianOyQxvi-OWasVEGegdLk-MOI/pub)







