---
output:
  knitrBootstrap::bootstrap_document:
    theme.chooser: TRUE
    highlight.chooser: TRUE
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{yummly}
%\VignetteDepends{xtable}
-->


### Cuisine Classification ###
Goal: Predict Cuisine type from an Ingredient list

####Training data####

```{r basicYummlyData, eval=TRUE,cache=TRUE,message=FALSE,warning=FALSE}
library(jsonlite)
download.file("http://s3.amazonaws.com/public-sparkbeyond/yummly.json.gz","./yummly.json.gz")
yummlyData = sampleData(fromJSON(readLines("./yummly.json.gz")), 0.3)
print(yummlyData[1, c("cuisine","ingredients")])
```

```{r basicYummlyModel, eval=TRUE, message=FALSE, results = 'hide',cache=TRUE}
yummlyModel=learn(
	projectName="Yummly",
	trainData = yummlyData,
	target = "cuisine",
	featureGeneration = featureGenerationControl(maxFeaturesCount = list(50))
)
```

<br>

####Top features####

```{r basicYummlyFeatures, eval=TRUE, results='asis', cache=TRUE}
print(xtable(yummlyModel$features()[1:5,c("RIG", "feature")]), type='html', comment=F) 
```

<br>

####Evaluation####
```{r basicYummlyEval, eval=TRUE, message=FALSE, cache=TRUE}
evaluation = yummlyModel$evaluate()
```

<br><br>
###Countries Distance
Goal: Predict (calculate) the distance between two given countries

####Training data####
```{r country_distances_data, eval=TRUE, results='asis',cache=TRUE}
countriesDistance = getData("countries_distance")
print(xtable(head(countriesDistance,n=5)), type='html', comment=F)
```

####Pipeline####
```{r country_distances, eval=TRUE, message=FALSE,results = 'hide',cache=TRUE}
countryModel=learn(projectName="CountriesDistance",countriesDistance,"distance",
	featureGeneration = featureGenerationControl(maxFeaturesCount = list(50))
)
```
<br>

####Top features####

```{r country_distancesFeatures, eval=TRUE, results='asis', cache=TRUE}
print(xtable(countryModel$features()[1:5,c("RIG", "feature")]), type='html', comment=F) 
```

<br>

####Evaluation####
```{r country_distancesEval, eval=TRUE, message=FALSE, cache=TRUE}
evaluation = countryModel$evaluate()
```

<br><br>

### Spam Email

Goal: Predict whether or not an email contains spam based on given statistics (UCI)

####Training data####

```{r spamData, eval=TRUE, results='asis',cache=TRUE}
spam = getData("spambase")
print(xtable(head(spam[,1:7],n=5)), type='html', comment=F)
```

<br>

####Pipeline####
```{r spambase, eval=TRUE, message=FALSE,results = 'hide',cache=TRUE}
spamModel=learn(projectName="spambase",spam,"isSpam",
	featureGeneration = featureGenerationControl(maxFeaturesCount = list(50))
)
```

####Top features####

```{r spamFeatures, eval=TRUE, results='asis', cache=TRUE}
print(xtable(spamModel$features()[1:5,c("RIG", "feature","Lift.0","Lift.1")]), type='html', comment=F) 
```

<br>

####Evaluation####
```{r spamEval, eval=TRUE, message=FALSE, cache=TRUE}
evaluation = spamModel$evaluate()
```